Evaluating infectious disease forecasts with allocation scoring rules

### 2023-12-10 alloscore_manuscript/alloscore-application.Rnw
some language for the IAS section

The integrated allocation score summarizes allocation scores across a range of possible values of the constraint ($K$), possibly taking weights into account for different values of $K$ that might be more or less likely (Section \ref{sec:methods.detailed.integrated_allocation}).
This could be useful in situations where the actual constraint may not be known, or could only be specified as a probability distribution.

This also underscores the points above that allocation scores are highest where the observed value is hear the allocation constraint, but here we are holding the date/models fixed and varying K.

Allocation scores are fairly stable across a range of values for K, and therefore IAS is not very sensitive to the choice of distribution on K, and does not differ much from the regular old allocation score as long as that allocation score was computed at a reasonable choice of K.

>>>>

The integrated allocation score summarizes allocation scores across a range of possible values of the constraint ($K$), possibly taking weights into account for different values of $K$ that might be more or less likely (Section \ref{sec:methods.detailed.integrated_allocation}).
This could be useful in situations where the actual constraint may not be known, or could only be specified as a probability distribution.
Unlike in the above analyses where we conducted analyses assuming that $K$ was known to be 15,000, the analyses in this subsection are conducted assuming different distributions of $K$.

<<calc-tot-y>>=
tot_y <- slim_alloscore_2021.12.20 |>
  filter(model == "COVIDhub-ensemble", K==200) |>
  pull(y) |>
  sum()
@

Allocation scores (AS) were computed for a range of $K$ from 200 to 60,000 for forecasts made on 2020-12-20 predicting levels of hospitalizations on 2021-01-03 (Figure \ref{fig:multi-k}A).
These calculations highlight that allocation scores were highest at the $K$ nearest to the observed value of \Sexpr{format(tot_y, big.mark = ",")}.
Rankings of allocation scores from all models were fairly stable across a range of values for K, with some crossings, especially at $K$ values further away from the observed value.

Integrated allocation scores (IAS) were computed for two distributions of $K$, one uniform across the entire range and the other a symmetric distribution around 15,000 (Figure \ref{fig:multi-k}B).
Both versions of the IAS were correlated with the original AS conducted at $K=15,000$, with the higher correlation coming from the distribution that was centered at $K=15,000$ (Figure \ref{fig:multi-k}C).
